---
title: "Final_Assignment _Cattoi_v3"
author: "Carlos Cattoi"
date: "31 de julho de 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load Needed libraries
```{needed libraries}
library(caret)
library(randomForest)
library(rpart)
library(rattle)
```

Setting seed
```{r set seed to 123}
set.seed(123)
```

Loading data into R
```{r load data}
trainingData <- read.csv("pml-training.csv", na.strings=c("NA","#DIV/0!",""))
testingData <- read.csv("pml-testing.csv", na.strings=c("NA","#DIV/0!",""))
str(trainingData)
```

Clean trainingData, removing unecessary Columns
```{r Cleaning 1}
UnecessaryColumns <- c('X','user_name','raw_timestamp_part_1','raw_timestamp_part_2','cvtd_timestamp','new_window', "num_window")
trainingData <- trainingData[,!(names(trainingData) %in% UnecessaryColumns)]
dim(trainingData)
```

Define the columns that has NZV and take off from original Train Data
```{nearZeroVar}
nzvColumns <- nearZeroVar(trainingData)
trainingData <- trainingData[,-nzvColumns]
dim(trainingData)

```

Take  off columns with too  many NAs (50%)
```{r Cleaning NA}
trainingData <- trainingData[,colSums(is.na(trainingData))<nrow(trainingData)*0.5]
dim(trainingData)

```

The training set must be divided into 2 new sets (70% Train  ;  30% Test)
```{createDataPartition}
inTrain <- createDataPartition(y=trainingData$classe, p=0.7, list=FALSE)
myTrain <- trainingData[inTrain, ]
myTest <- trainingData[-inTrain, ]
dim(myTrain)
dim(myTest)

```


Predictong using Decision Tree
```{Predicting using Decision Tree}
#Fit a model and plot a decicion Tree using 'rpart'
modelFitDT <- rpart(classe ~ ., data=myTrain, method="class")
fancyRpartPlot(modelFitDT)

#Predict Using ModelFit1
predictionDT <- predict(modelFitDT, myTest, type = "class")

#Check confusion matrix results for predictionDT
confusionMatrix(predictionDT, myTest$classe)

```

Predict using Random forests
```{Predict using Random forests}
#Fit a model by Random Forests
modelFitRF <- randomForest(classe ~. , data=myTrain)

#Predicting a model  by random  forest
predictionRF <- predict(modelFitRF, myTest, type = "class")

#Check confusion matrix results for prediction1
confusionMatrix(predictionRF, myTest$classe)

```

Since RandomForest Accuracy is 99,4%; we'll use modelFitRF to predict our trainingData
```{Applying on Testing Data}
testingData<-testingData[,intersect(names(trainingData),names(testingData))] 
prediction_Testing <- predict(modelFitRF, testingData)
```

final prediction files area created
```{creating the final prediction files}
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}

pml_write_files(prediction_Testing)
```